Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
Added margin comments
Added more margin comments

\vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}

@@

\subsubsection{A quotient of a Frobenius category}
\begin{example}
 Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.  It is a self-injective algebra, so its module category is a Frobenius category.  Its projective-injective objects are the modules 
 \[
  \begin{matrix} 1 \\ 2 \\ 3 \end{matrix} \quad , \quad  \begin{matrix} 2 \\ 13 \\ 2 \end{matrix} \quad \textrm{and} \quad \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}.
 \]
 Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category whose Auslander--Reiten quiver is given by
  \[
  \hspace*{-2cm}
 {\footnotesize
  \begin{tikzcd}
   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
    & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
  \end{tikzcd}
  }
 \]
 \pg{To finish}
\end{example}

>>>>

\vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}
\pg{It is done in Coro~\ref{coro::exchangeablePairsNKC}.}

@@

\subsubsection{A quotient of a Frobenius category}
\begin{example}
 Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.  It is a self-injective algebra, so its module category is a Frobenius category.  Its projective-injective objects are the modules 
 \[
  \begin{matrix} 1 \\ 2 \\ 3 \end{matrix} \quad , \quad  \begin{matrix} 2 \\ 13 \\ 2 \end{matrix} \quad \textrm{and} \quad \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}.
 \]
 Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category~\cite{} whose Auslander--Reiten quiver is given as follows.
  \[
  \hspace*{-2cm}
 {\footnotesize
  \begin{tikzcd}
   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
    & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
  \end{tikzcd}
  }
 \]

 \pg{Not sure why we wanted this example anymore.}
\end{example}
